\documentclass{letter}

% Preamble
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{setspace}
\setstretch{1.15}
\usepackage[hidelinks]{hyperref}
\begin{document}

\begin{flushleft}
    \textbf{Harikesh Kushwaha}\\
    New Delhi, Delhi, 110016\\
    \href{mailto:harikeshkumar0926@gmail.com}{harikeshkumar0926@gmail.com}\\
    \today
\end{flushleft}

\begin{center}
    \textbf{Application for the Position of Data Scientist at Capgemini, Bangaluru}
\end{center}

Dear Hiring Manager,

I am writing to express my interest in the position of Data Scientist at Capgemini, Bangaluru. As a recent graduate, having a strong foundation in machine learning, statistics, and data analysis, I am excited about the opportunity to apply my skills to real-world business problems.

Although I am a fresher in the field of data science, I have completed several data science projects during my studies, including exploratory data analysis, predictive modeling, and data visualization. I am confident that these experiences have equipped me with the necessary technical skills, including programming languages such as SQL and Python, and data visualization tools such as Tableau and Power BI. I have also very good knowledge of deep learning architectures in computor vision and NLP. I've worked on a number of projects using these architectures and I am sure that I can use these skills in the position.

Moreover, I have excellent communication skills, both written and verbal, which would enable me to communicate effectively with stakeholders and explain complex data science concepts in a way that is understandable to non-technical stakeholders. Additionally, I am a quick learner and passionate about the field of data science, and I am willing to take on new challenges to upskill myself in the field.

I would be honored to join your team and I am confident that I can contribute to the team's success and deliver high-quality work.

Thank you for considering my application. I look forward to the opportunity to discuss my candidacy further.


Sincerely,\\
\textbf{Harikesh Kushwaha}

\end{document}
