\documentclass{letter}

% Preamble
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{setspace}
\setstretch{1.15}
\usepackage[hidelinks]{hyperref}
\begin{document}

\begin{flushleft}
    \textbf{Harikesh Kushwaha}\\
    New Delhi, Delhi, 110016\\
    \href{mailto:harikeshkumar0926@gmail.com}{harikeshkumar0926@gmail.com}\\
    \today
\end{flushleft}

\begin{center}
    \textbf{Application for the Position of Manager Data Science at Adidas Gurgaon Tech Hub}
\end{center}

Dear Hiring Manager,

I am writing to express my interest in the position of Manager Data Science at Adidas Gurgaon Tech Hub. As a recent graduate, having a strong foundation in machine learning, statistics, and data analysis, I am excited about the opportunity to apply my skills to real-world business problems.

Although I am a fresher in the field of data science, I have completed several data science projects during my studies, including exploratory data analysis, predictive modeling, and data visualization. I am confident that these experiences have equipped me with the necessary technical skills, including programming languages such as SQL and Python, and data visualization tools such as Tableau and Power BI.

Moreover, I have excellent communication skills, both written and verbal, which would enable me to communicate effectively with stakeholders and explain complex data science concepts in a way that is understandable to non-technical stakeholders. Additionally, I am a quick learner and passionate about the field of data science, and I am willing to take on new challenges to upskill myself in the field.

I would be honored to join your team and work with the EU eCom Analytics team and other stakeholders located in different parts of the world. I am confident that I can contribute to the team's success and deliver high-quality work.

Thank you for considering my application. I look forward to the opportunity to discuss my candidacy further.


Sincerely,\\
\textbf{Harikesh Kushwaha}

\end{document}
