%-----------PROJECTS--------------------------
% Use resumeQuadHeading if four elements are feasible (ex: demo video link), else use resumeTrioHeading. Keep the bullet points simple and concise and try to cover wide variety of skills you have used to build these projects

\section{Projects}
\resumeHeadingListStart{}

% House Prices - Advanced Regression Techniques
\resumeTrioHeading{House Prices Prediction}{Python, pandas, scikit-learn, kaggle, Matplotlib, Seaborn}{\href{https://github.com/Hari31416/Portfolio/tree/main/ML/Housing_Price}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Analyzed over \textbf{80} features to predict house prices using machine learning.}
\resumeItem{Performed \textbf{data visualization} and \textbf{feature engineering} using Matplotlib and Seaborn, respectively.}
\resumeItem{Trained \textbf{multiple models} using scikit-learn and selected the best one by applying \textbf{grid search} and \textbf{cross-validation}. Achieved a \textbf{top 12\%} ranking on the Kaggle leaderboard.}
\resumeItemListEnd{}

% Digit Recognizer
\resumeTrioHeading{Digit Recognizer}{Python, TensorFlow, Keras, Kaggle}{\href{https://github.com/Hari31416/Portfolio/tree/main/DL/MNIST_Digits}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Developed a very deep \textbf{convolutional neural network} using TensorFlow and Keras with \textbf{dropout} and \textbf{batch normalization} to improve performance.}
\resumeItem{Achieved an accuracy of \textbf{99.48\%} on the test set, securing a place in the \textbf{top 15\%} on the Kaggle leaderboard.}
\resumeItem{Deployed the app on \textbf{HuggingFace} using \textbf{Gradio} and made it available to the public. Find the app \href{https://huggingface.co/spaces/hari31416/digit_recognizer}{\link{here}}.}
\resumeItemListEnd{}


% Food Vision
\resumeTrioHeading{Food Vision}{Python, TensorFlow, Colab}{\href{https://github.com/Hari31416/Portfolio/tree/main/DL/Food\%20Vision}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Developed a deep \textbf{neural network} using TensorFlow and Keras to classify \textbf{101 categories of food}.}
\resumeItem{Used a pretrained \textbf{EfficientNet} model to extract features from the food images, and then \textbf{fine-tuned} the model to improve its accuracy.}
\resumeItem{Achieved an accuracy of \textbf{80\%} on the test set, demonstrating the effectiveness of the approach in addressing complex image recognition problems.}
\resumeItemListEnd{}


% Natural Language Processing with Disaster Tweets
\resumeTrioHeading{NLP With Disaster Tweets}{Python, TensorFlow, NLP, Text Vectorization, LSTM, GRU, CNN}{\href{https://github.com/Hari31416/Portfolio/tree/main/ML/Disaster_Tweets}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Developed NLP models to classify disaster and non-disaster tweets using \textbf{text vectorization}, various \textbf{word embeddings}, and deep learning models including \textbf{LSTM}, \textbf{GRU}, their \textbf{bidirectional} variants, and \textbf{1D CNNs}}
\resumeItem{Utilized the \textbf{Universal Sentence Encoder} to create embeddings on both the character and word levels, and implemented a \textbf{multivariate} model using the \textbf{functional API} of \textbf{TensorFlow}.}
\resumeItemListEnd{}


% TensorFlow Speech Recognition Challenge
\resumeTrioHeading{TensorFlow Speech Recognition Challenge}{Python, pandas, TensorFlow, kaggle}{\href{https://github.com/Hari31416/Portfolio/tree/main/DL/TensorFlow_Speech_Recognition}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Trained a deep neural network to recognize \textbf{30} different commands by creating waveforms and transforming them into \textbf{2D spectrograms} using STFT.}
\resumeItem{Used a convolutional neural network architecture and achieved an \textbf{accuracy of about 90\%} on the test set.}
\resumeItemListEnd{}

% Titanic - Machine Learning from Disaster
\resumeTrioHeading{Titanic - Machine Learning from Disaster}{Python, pandas, sklearn, kaggle}{\href{https://github.com/Hari31416/Portfolio/tree/main/ML/Titanic}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Analyzed the Titanic dataset and performed \textbf{data cleaning}, \textbf{feature engineering}, and \textbf{data visualization}.}
\resumeItem{Built several machine learning models including \textbf{Logistic Regression}, \textbf{Random Forest}, and \textbf{Gradient Boosting} and selected the best model using \textbf{cross-validation}.}
\resumeItem{Achieved a test accuracy of \textbf{78.5\%}, which was in the \textbf{top 12\%} of the Kaggle leaderboard at the time.}
\resumeItemListEnd{}

% NNet
\resumeTrioHeading{NNet}{Python, NumPy, Neural Network}{\href{https://github.com/Hari31416/NNet}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Developed a module for arbitrary neural network architecture using \textbf{Python} and \textbf{NumPy}, implementing layers such as \textbf{Dense}, \textbf{Dropout}, \textbf{Conv2D}, \textbf{Flatten}, \textbf{Reshape} etc.}
\resumeItem{Implemented both the forward and backward pass of the layers, demonstrating proficiency in \textbf{backpropagation} and \textbf{gradient descent}.}
\resumeItem{Created an API similar to \textbf{Keras} for seamless integration and implemented various activation functions including \textbf{ReLU}, \textbf{tanh}, \textbf{sigmoid}, and \textbf{softmax}.}
\resumeItem{Demonstrated strong skills in \textbf{machine learning}, \textbf{Python programming}, and \textbf{mathematics} while gaining a deeper understanding of the inner workings of neural networks.}
\resumeItemListEnd{}

% ReVision
\resumeTrioHeading{ReVision}{Python, NumPy, TensorFlow, PyTorch, CLI}{\href{https://github.com/Hari31416/ReVision}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Created a personal project called \textbf{ReVision} to learn the concepts and implementation details of groundbreaking \textbf{computer vision papers}.}
\resumeItem{Utilized popular deep learning frameworks such as \textbf{TensorFlow} and \textbf{PyTorch} to implement the architectures of seminal papers like \textbf{LeNet}, \textbf{AlexNet}, \textbf{VGG}, \textbf{ResNet}, \textbf{Inception}, \textbf{EfficientNet}, etc.}
\resumeItem{Developed a deep understanding of the underlying principles of deep learning and computer vision, while improving skills in \textbf{Python programming}, \textbf{machine learning}, and \textbf{deep learning}.}
\resumeItem{Demonstrated proficiency in various computer vision tasks, such as \textbf{image classification}, \textbf{object detection}, and \textbf{semantic segmentation}.}
\resumeItemListEnd{}

% IBM Data Analytics
% More techs: Web Scraping, Web API, dashboard, presentation, BI 
\resumeTrioHeading{IBM Data Analytics Capstone Project}{Python, pandas, Matplotlib, Web Scraping, Web API}{\href{https://github.com/Hari31416/Portfolio/tree/main/ML/Housing_Price}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Gathered and analyzed data from various sources, including \textbf{API} and \textbf{web scraping}. Conducted \textbf{exploratory data analysis} and \textbf{wrangling} to prepare the data for further analysis.}
\resumeItem{Built a \textbf{dynamic dashboard} to extract valuable insights from the collected data, and effectively \textbf{communicated} the findings to others through an \textbf{engaging presentation}.}
\resumeItemListEnd{}

% Credit Risk Assesment
% More techs: matplotlib, pandas, seaborn
\resumeTrioHeading{Credit Risk Assesment}{Python, pandas, scikit-learn, kaggle}{\href{https://github.com/Hari31416/Portfolio/tree/main/ML/Housing_Price}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Developed a credit textbf{risk assessment} model by analyzing various customer features, performing data cleaning, feature engineering, and exploratory data analysis. }
\resumeItem{Established a basic model for initial experimentation, and trained advanced models such as \textbf{LR}, \textbf{SVM}, \textbf{XGBoost}, \textbf{Catboost}. Top performing model, achieved a test AUC-ROC score of \textbf{0.97} and precision of \textbf{0.96}.}
\resumeItemListEnd{}

%pystock
\resumeTrioHeading{\href{https://pypi.org/project/pystock0/}{\link{pystock}}}{Python, portfolio theory, pytest}{\href{https://github.com/Hari31416/pystock}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Developed \textbf{pystock}, a comprehensive \textbf{Python library} for \textbf{portfolio optimization} and management. Utilizing \textbf{object-oriented programming}, created a \textbf{user-friendly API} capable of optimizing portfolios with any number of securities.}
\resumeItem{The library includes various models, such as the \textbf{Capital Asset Pricing Model, Single Index Model}, \textbf{Fama-French three-} and \textbf{five-factor models}, and has a suite of over \textbf{100 unit tests} written with \textbf{pytest and fixtures}, spanning more than \textbf{1500 lines of code}.}
\resumeItemListEnd{}


%optionalyzer
\resumeTrioHeading{optionalyzer}{Python, options, futures, plotly, BS model}{\href{https://github.com/Hari31416/Finance/tree/main/Projects/optionalyzer}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Developed \textbf{optionalyzer}, a powerful \textbf{Python library} for \textbf{Options Strategy Builder} that makes it easy to create custom options trading strategies.}
\resumeItem{Implemented the \textbf{Black-Scholes Model} to accurately calculate \textbf{Option prices} and utilized \textbf{optimization} techniques to find the \textbf{implied volatility} of the Option, enabling users to make better trading decisions.}
\resumeItem{Leveraged \textbf{Plotly} to create an \textbf{interactive Options payoff diagram} for any date, allowing users to explore potential outcomes for different combinations of Options.}
\resumeItem{Developed a \textbf{user-friendly API} that enables users to easily add \textbf{short or long}, \textbf{Put and Call Options} to the payoff diagram for strategy building.}
\resumeItemListEnd{}

%frontier
\resumeTrioHeading{frontier}{Python, portfolio theory, pytest}{\href{https://github.com/Hari31416/Finance/tree/main/Projects/frontier}{\link{Source Code}}}
\resumeItemListStart{}
\resumeItem{Developed \textbf{frontier}, a Python module for \textbf{plotting the efficient frontier} of a portfolio with an arbitrary number of securities.}
\resumeItem{Utilizes \textbf{Monte Carlo simulations} to create an \textbf{interactive efficient frontier}, enabling users to easily explore different portfolios and their expected returns and risks.}
\resumeItem{Built on top of \textbf{pystock}, the module supports all the models that are supported by pystock, including \textbf{CAPM, SIM, FF3FM} and \textbf{FF5FM}, making it a comprehensive tool for portfolio optimization and management.}
\resumeItemListEnd{}

% Tableau
\resumeTrioHeading{Tableau Dashboards}{Tableau, Web Scraping, Web API, BeautifulSoup}{\href{https://public.tableau.com/app/profile/hari31416/viz/Spotifyin2022/SummaryAndTaylorSupremacy}{\link{Music}} \href{https://public.tableau.com/app/profile/hari31416/viz/Booksin2022/MyBooksin2022}{\link{Books}}}
\resumeItemListStart{}
\resumeItem{Created an interactive \textbf{Tableau} \textbf{viz} showcasing my \textbf{Spotify} \textbf{streaming history} over several years, using \textbf{data blending} and \textbf{calculated fields} to present key insights.}
\resumeItem{Utilized \textbf{web scraping} techniques to extract my book reading history from \textbf{Goodreads} and created an interactive \textbf{Tableau} dashboard to analyze and visualize the data.}
\resumeItemListEnd{}

\resumeHeadingListEnd{}
