%-----------PROJECTS--------------------------
% Use resumeQuadHeading if four elements are feasible (ex: demo video link), else use resumeTrioHeading. Keep the bullet points simple and concise and try to cover wide variety of skills you have used to build these projects

\section{Projects}
\resumeHeadingListStart{}

% House Prices - Advanced Regression Techniques
\resumeTrioHeading{House Prices Prediction}{Python, pandas, scikit-learn, kaggle, Matplotlib, Seaborn}{\href{https://github.com/Hari31416/Portfolio/tree/main/ML/Housing_Price}{\uline{Source Code}}}
\resumeItemListStart{}
\resumeItem{Analyzed over \textbf{80} features to predict house prices using machine learning.}
\resumeItem{Performed \textbf{data visualization} and \textbf{feature engineering} using Matplotlib and Seaborn, respectively.}
\resumeItem{Trained \textbf{multiple models} using scikit-learn and selected the best one by applying \textbf{grid search} and \textbf{cross-validation}. Achieved a \textbf{top 12\%} ranking on the Kaggle leaderboard.}
\resumeItemListEnd{}

% IBM Data Analytics
% More techs: Web Scraping, Web API, dashboard, presentation, BI 
\resumeTrioHeading{IBM Data Analytics Capstone Project}{Python, pandas, Matplotlib, Web Scraping, Web API}{\href{https://github.com/Hari31416/Portfolio/tree/main/ML/Housing_Price}{\uline{Source Code}}}
\resumeItemListStart{}
\resumeItem{Gathered and analyzed data from various sources, including \textbf{API} and \textbf{web scraping}. Conducted \textbf{exploratory data analysis} and \textbf{wrangling} to prepare the data for further analysis.}
\resumeItem{Built a \textbf{dynamic dashboard} to extract valuable insights from the collected data, and effectively \textbf{communicated} the findings to others through an \textbf{engaging presentation}.}
\resumeItemListEnd{}

% Credit Risk Assesment
% More techs: matplotlib, pandas, seaborn
\resumeTrioHeading{Credit Risk Assesment}{Python, pandas, scikit-learn, kaggle}{\href{https://github.com/Hari31416/Portfolio/tree/main/ML/Housing_Price}{\uline{Source Code}}}
\resumeItemListStart{}
\resumeItem{Developed a credit textbf{risk assessment} model by analyzing various customer features, performing data cleaning, feature engineering, and exploratory data analysis. }
\resumeItem{Established a basic model for initial experimentation, and trained advanced models such as \textbf{LR}, \textbf{SVM}, \textbf{XGBoost}, \textbf{Catboost}. Top performing model, achieved a test AUC-ROC score of \textbf{0.97} and precision of \textbf{0.96}.}
\resumeItemListEnd{}

%pystock
\resumeTrioHeading{\href{https://pypi.org/project/pystock0/}{\uline{pystock}}}{Python, portfolio theory, pytest}{\href{https://github.com/Hari31416/pystock}{\uline{Source Code}}}
\resumeItemListStart{}
\resumeItem{Developed \textbf{pystock}, a comprehensive \textbf{Python library} for \textbf{portfolio optimization} and management. Utilizing \textbf{object-oriented programming}, created a \textbf{user-friendly API} capable of optimizing portfolios with any number of securities.}
\resumeItem{The library includes various models, such as the \textbf{Capital Asset Pricing Model, Single Index Model}, \textbf{Fama-French three-} and \textbf{five-factor models}, and has a suite of over \textbf{100 unit tests} written with \textbf{pytest and fixtures}, spanning more than \textbf{1500 lines of code}.}
\resumeItemListEnd{}

%optionalyzer
\resumeTrioHeading{optionalyzer}{Python, options, futures, plotly, BS model}{\href{https://github.com/Hari31416/Finance/tree/main/Projects/optionalyzer}{\uline{Source Code}}}
\resumeItemListStart{}
\resumeItem{Developed \textbf{optionalyzer}, a powerful \textbf{Python library} for \textbf{Options Strategy Builder} that makes it easy to create custom options trading strategies.}
\resumeItem{Implemented the \textbf{Black-Scholes Model} to accurately calculate \textbf{Option prices} and utilized \textbf{optimization} techniques to find the \textbf{implied volatility} of the Option, enabling users to make better trading decisions.}
\resumeItem{Leveraged \textbf{Plotly} to create an \textbf{interactive Options payoff diagram} for any date, allowing users to explore potential outcomes for different combinations of Options.}
\resumeItem{Developed a \textbf{user-friendly API} that enables users to easily add \textbf{short or long}, \textbf{Put and Call Options} to the payoff diagram for strategy building.}
\resumeItemListEnd{}

%frontier
\resumeTrioHeading{frontier}{Python, portfolio theory, pytest}{\href{https://github.com/Hari31416/Finance/tree/main/Projects/frontier}{\uline{Source Code}}}
\resumeItemListStart{}
\resumeItem{Developed \textbf{frontier}, a Python module for \textbf{plotting the efficient frontier} of a portfolio with an arbitrary number of securities.}
\resumeItem{Utilizes \textbf{Monte Carlo simulations} to create an \textbf{interactive efficient frontier}, enabling users to easily explore different portfolios and their expected returns and risks.}
\resumeItem{Built on top of \textbf{pystock}, the module supports all the models that are supported by pystock, including \textbf{CAPM, SIM, FF3FM} and \textbf{FF5FM}, making it a comprehensive tool for portfolio optimization and management.}
\resumeItemListEnd{}

% Tableau
\resumeTrioHeading{Tableau Dashboards}{Tableau, Web Scraping, Web API, BeautifulSoup}{\href{https://public.tableau.com/app/profile/hari31416/viz/Spotifyin2022/SummaryAndTaylorSupremacy}{\uline{Music}} \href{https://public.tableau.com/app/profile/hari31416/viz/Booksin2022/MyBooksin2022}{\uline{Books}}}
\resumeItemListStart{}
\resumeItem{Created an interactive \textbf{Tableau} \textbf{viz} showcasing my \textbf{Spotify} \textbf{streaming history} over several years, using \textbf{data blending} and \textbf{calculated fields} to present key insights.}
\resumeItem{Utilized \textbf{web scraping} techniques to extract my book reading history from \textbf{Goodreads} and created an interactive \textbf{Tableau} dashboard to analyze and visualize the data.}
\resumeItemListEnd{}

\resumeHeadingListEnd{}